---
title: "RepeatedConcordance"
author: "Aditya Ponnada"
date: "July 21, 2018"
output: html_document
editor_options: 
  chunk_output_type: inline
---

#### Import libraries
```{r}
library(dplyr)
library(plyr)
library(MASS)
library(psych)
library(rmcorr)
library(cccrm)
library(caret)
library(irr)
```

#### read predictions mapping file - 10s
```{r}
filePath = "C:/Users/Dharam/Downloads/microEMA/StudyFiles/CombinedData/predictions_10.csv"

predictionsMap <- read.csv(filePath, sep = ",", header = TRUE)

head(predictionsMap)
tail(predictionsMap)


### Remove NAs from the ankle before and after columns
# predictionsMap <- predictionsMap[!is.na(predictionsMap$COUNTS_SUM_ANKLE_BEFORE),]
# combinedFile <- combinedFile[!is.na(combinedFile$COUNTS_SUM_ANKLE_AFTER),]

### Convert prompt time to date time object
predictionsMap$PROMPT_TIME <- as.POSIXct(predictionsMap$PROMPT_TIME, format = "%Y-%m-%d %H:%M:%OS")
```

#### Repeated concordance measure
```{r}
# ccclon(predictionsMap,PREDICTED_ACTIVITY_TYPE, ACTIVITY_TYPE, USER_ID, covar = NULL, rho = 0, cl = 0.95)

##y10
```

#### Get confusion matrices

```{r}

keep <- c("ACTIVITY_TYPE", "PREDICTED_ACTIVITY_TYPE")



u <- union(predictionsMap$ACTIVITY_TYPE,predictionsMap$PREDICTED_ACTIVITY_TYPE)
t <- table(factor(predictionsMap$ACTIVITY_TYPE, u), factor(predictionsMap$PREDICTED_ACTIVITY_TYPE, u))
y10 <- confusionMatrix(t)

y10
```

#### read predictions mapping file - 30s
```{r}
filePath = "C:/Users/Dharam/Downloads/microEMA/StudyFiles/CombinedData/predictions_30.csv"

predictionsMap <- read.csv(filePath, sep = ",", header = TRUE)

head(predictionsMap)
tail(predictionsMap)


### Remove NAs from the ankle before and after columns
# predictionsMap <- predictionsMap[!is.na(predictionsMap$COUNTS_SUM_ANKLE_BEFORE),]
# combinedFile <- combinedFile[!is.na(combinedFile$COUNTS_SUM_ANKLE_AFTER),]

### Convert prompt time to date time object
predictionsMap$PROMPT_TIME <- as.POSIXct(predictionsMap$PROMPT_TIME, format = "%Y-%m-%d %H:%M:%OS")
```

#### Get confusion matrices

```{r}

keep <- c("ACTIVITY_TYPE", "PREDICTED_ACTIVITY_TYPE")



u <- union(predictionsMap$ACTIVITY_TYPE,predictionsMap$PREDICTED_ACTIVITY_TYPE)
t <- table(factor(predictionsMap$ACTIVITY_TYPE, u), factor(predictionsMap$PREDICTED_ACTIVITY_TYPE, u))
y30 <- confusionMatrix(t)

y30
```

#### read predictions mapping file - 60s
```{r}
filePath = "C:/Users/Dharam/Downloads/microEMA/StudyFiles/CombinedData/predictions_60.csv"

predictionsMap <- read.csv(filePath, sep = ",", header = TRUE)

head(predictionsMap)
tail(predictionsMap)


### Remove NAs from the ankle before and after columns
# predictionsMap <- predictionsMap[!is.na(predictionsMap$COUNTS_SUM_ANKLE_BEFORE),]
# combinedFile <- combinedFile[!is.na(combinedFile$COUNTS_SUM_ANKLE_AFTER),]

### Convert prompt time to date time object
predictionsMap$PROMPT_TIME <- as.POSIXct(predictionsMap$PROMPT_TIME, format = "%Y-%m-%d %H:%M:%OS")
```

#### Get confusion matrices

```{r}

keep <- c("ACTIVITY_TYPE", "PREDICTED_ACTIVITY_TYPE")



u <- union(predictionsMap$ACTIVITY_TYPE,predictionsMap$PREDICTED_ACTIVITY_TYPE)
t <- table(factor(predictionsMap$ACTIVITY_TYPE, u), factor(predictionsMap$PREDICTED_ACTIVITY_TYPE, u))
y60 <- confusionMatrix(t)

y60
```

#### read predictions mapping file - 150s
```{r}
filePath = "C:/Users/Dharam/Downloads/microEMA/StudyFiles/CombinedData/predictions_150.csv"

predictionsMap <- read.csv(filePath, sep = ",", header = TRUE)

head(predictionsMap)
tail(predictionsMap)


### Remove NAs from the ankle before and after columns
# predictionsMap <- predictionsMap[!is.na(predictionsMap$COUNTS_SUM_ANKLE_BEFORE),]
# combinedFile <- combinedFile[!is.na(combinedFile$COUNTS_SUM_ANKLE_AFTER),]

### Convert prompt time to date time object
predictionsMap$PROMPT_TIME <- as.POSIXct(predictionsMap$PROMPT_TIME, format = "%Y-%m-%d %H:%M:%OS")
```

#### Get confusion matrices

```{r}

keep <- c("ACTIVITY_TYPE", "PREDICTED_ACTIVITY_TYPE")



u <- union(predictionsMap$ACTIVITY_TYPE,predictionsMap$PREDICTED_ACTIVITY_TYPE)
t <- table(factor(predictionsMap$ACTIVITY_TYPE, u), factor(predictionsMap$PREDICTED_ACTIVITY_TYPE, u))
y150 <- confusionMatrix(t)

y150
```

#### read predictions mapping file - 300s
```{r}
filePath = "C:/Users/Dharam/Downloads/microEMA/StudyFiles/CombinedData/predictions_300.csv"

predictionsMap <- read.csv(filePath, sep = ",", header = TRUE)

head(predictionsMap)
tail(predictionsMap)


### Remove NAs from the ankle before and after columns
# predictionsMap <- predictionsMap[!is.na(predictionsMap$COUNTS_SUM_ANKLE_BEFORE),]
# combinedFile <- combinedFile[!is.na(combinedFile$COUNTS_SUM_ANKLE_AFTER),]

### Convert prompt time to date time object
predictionsMap$PROMPT_TIME <- as.POSIXct(predictionsMap$PROMPT_TIME, format = "%Y-%m-%d %H:%M:%OS")
```

#### Get confusion matrices

```{r}

keep <- c("ACTIVITY_TYPE", "PREDICTED_ACTIVITY_TYPE")



u <- union(predictionsMap$ACTIVITY_TYPE,predictionsMap$PREDICTED_ACTIVITY_TYPE)
t <- table(factor(predictionsMap$ACTIVITY_TYPE, u), factor(predictionsMap$PREDICTED_ACTIVITY_TYPE, u))
y300 <- confusionMatrix(t)

y300
```

#### read predictions mapping file - 600s
```{r}
filePath = "C:/Users/Dharam/Downloads/microEMA/StudyFiles/CombinedData/predictions_600.csv"

predictionsMap <- read.csv(filePath, sep = ",", header = TRUE)

head(predictionsMap)
tail(predictionsMap)


### Remove NAs from the ankle before and after columns
# predictionsMap <- predictionsMap[!is.na(predictionsMap$COUNTS_SUM_ANKLE_BEFORE),]
# combinedFile <- combinedFile[!is.na(combinedFile$COUNTS_SUM_ANKLE_AFTER),]

### Convert prompt time to date time object
predictionsMap$PROMPT_TIME <- as.POSIXct(predictionsMap$PROMPT_TIME, format = "%Y-%m-%d %H:%M:%OS")
```


#### Get confusion matrices

```{r}

keep <- c("ACTIVITY_TYPE", "PREDICTED_ACTIVITY_TYPE")



u <- union(predictionsMap$ACTIVITY_TYPE,predictionsMap$PREDICTED_ACTIVITY_TYPE)
t <- table(factor(predictionsMap$ACTIVITY_TYPE, u), factor(predictionsMap$PREDICTED_ACTIVITY_TYPE, u))
y600 <- confusionMatrix(t)

y600
```

```{r}
library(ordinal)

predictionsMap$ACTIVITY_ORDINAL[predictionsMap$ACTIVITY_TYPE == "Sedentary"] <- 1
predictionsMap$ACTIVITY_ORDINAL[predictionsMap$ACTIVITY_TYPE == "Light/Standing"] <- 2
predictionsMap$ACTIVITY_ORDINAL[predictionsMap$ACTIVITY_TYPE == "Moderate/Walking"] <- 3
predictionsMap$ACTIVITY_ORDINAL[predictionsMap$ACTIVITY_TYPE == "Vigorous"] <- 4

head(predictionsMap)



predictionsMap$PREDICTED_ORDINAL[predictionsMap$PREDICTED_ACTIVITY_TYPE == "Sedentary"] <- 1
predictionsMap$PREDICTED_ORDINAL[predictionsMap$PREDICTED_ACTIVITY_TYPE == "Light/Standing"] <- 2
predictionsMap$PREDICTED_ORDINAL[predictionsMap$PREDICTED_ACTIVITY_TYPE == "Moderate/Walking"] <- 3
predictionsMap$PREDICTED_ORDINAL[predictionsMap$PREDICTED_ACTIVITY_TYPE == "Vigorous"] <- 4

head(predictionsMap)


predictionsMap$ACTIVITY_ORDINAL <- factor(predictionsMap$ACTIVITY_ORDINAL, ordered = T)

predictionsMap$PREDICTED_ORDINAL <- factor(predictionsMap$PREDICTED_ORDINAL, ordered = T)


class(predictionsMap$ACTIVITY_ORDINAL)
levels(predictionsMap$ACTIVITY_ORDINAL)

class(predictionsMap$PREDICTED_ORDINAL)
levels(predictionsMap$PREDICTED_ORDINAL)

```

```{r}
model1 <- clmm(PREDICTED_ORDINAL~ACTIVITY_ORDINAL + (1|USER_ID), data = predictionsMap, Hess = T, nAGQ = 1)

model1

summary(model1)
```

