---
title: "Ordinal Logistic Regression"
author: "Aditya Ponnada"
date: "June 16, 2018"
output: html_document
editor_options: 
  chunk_output_type: inline
---

#### Import libraries

```{r}
library(psych)
library(MASS)
library(reshape2)
library(plotly)
library(ggplot2)
library(ordinal)
library(lme4)
```


#### Read combined uEMA counts file

```{r}
path = "C:/Users/Dharam/Downloads/microEMA/StudyFiles/CombinedData/tenSecMappedData.csv"

uEMAComboFile <- read.csv(path, sep = ",", header = TRUE)

head(uEMAComboFile)
tail(uEMAComboFile)
```

#### Convert date time columns to date time objects

```{r}
### Remove NAs from the ankle before and after columns
uEMAComboFile <- uEMAComboFile[!is.na(uEMAComboFile$COUNTS_SUM_ANKLE_BEFORE),]
uEMAComboFile <- uEMAComboFile[!is.na(uEMAComboFile$COUNTS_SUM_ANKLE_AFTER),]

### Convert prompt time to date time object
uEMAComboFile$PROMPT_TIME <- as.POSIXct(uEMAComboFile$PROMPT_TIME, format = "%Y-%m-%d %H:%M:%OS")

head(uEMAComboFile)

```









#### Remove accelerometer non wear days from the file

```{r}
# uEMAComboFile <- uEMAComboFile[!(uEMAComboFile$USER_ID == "uema02@micropa_com" & ((uEMAComboFile$PROMPT_TIME > as.POSIXct("2018-02-10 07:00:00") & uEMAComboFile$PROMPT_TIME < as.POSIXct("2018-02-10 23:00:00")) | (uEMAComboFile$PROMPT_TIME > as.POSIXct("2018-02-12 07:00:00") & uEMAComboFile$PROMPT_TIME < as.POSIXct("2018-02-12 23:00:00")) | (uEMAComboFile$PROMPT_TIME > as.POSIXct("2018-02-22 07:00:00") & uEMAComboFile$PROMPT_TIME < as.POSIXct("2018-02-22 23:00:00")))),]
# 
# 
# uEMAComboFile <- uEMAComboFile[!(uEMAComboFile$USER_ID == "uema06@micropa_com" & ((uEMAComboFile$PROMPT_TIME > as.POSIXct("2018-02-24 00:00:00") & uEMAComboFile$PROMPT_TIME < as.POSIXct("2018-02-24 10:00:00")))),]
# 
# #### remove participant 17
# 
# ##uEMAComboFile <- uEMAComboFile[!(uEMAComboFile$USER_ID == "uema17@micropa_com"),]
```

#### Convert uEMA responses to ordinal responses

```{r}
uEMAComboFile$ACTIVITY_ORDINAL[uEMAComboFile$ACTIVITY_TYPE == "Sedentary"] <- 1
uEMAComboFile$ACTIVITY_ORDINAL[uEMAComboFile$ACTIVITY_TYPE == "Light/Standing"] <- 2
uEMAComboFile$ACTIVITY_ORDINAL[uEMAComboFile$ACTIVITY_TYPE == "Moderate/Walking"] <- 3
uEMAComboFile$ACTIVITY_ORDINAL[uEMAComboFile$ACTIVITY_TYPE == "Vigorous"] <- 4

head(uEMAComboFile)


uEMAComboFile$ACTIVITY_ORDINAL <- factor(uEMAComboFile$ACTIVITY_ORDINAL, ordered = T)
class(uEMAComboFile$ACTIVITY_ORDINAL)
levels(uEMAComboFile$ACTIVITY_ORDINAL)

```

#### Rescale (log transformation) of counts variable
```{r}
ggplot(data=uEMAComboFile, aes(uEMAComboFile$COUNTS_SUM_ANKLE_BEFORE)) + geom_histogram()

uEMAComboFile$COUNTS_LOG <- log(uEMAComboFile$COUNTS_SUM_ANKLE_BEFORE + 1)

ggplot(data=uEMAComboFile, aes(uEMAComboFile$COUNTS_LOG)) + geom_histogram()

uEMAComboFile$COUNTS_SQRT <- sqrt(uEMAComboFile$COUNTS_SUM_ANKLE_BEFORE)

ggplot(data=uEMAComboFile, aes(uEMAComboFile$COUNTS_SQRT)) + geom_histogram()

```

#### Convert UserID to numeric

```{r}
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema01@micropa_com"] <- "1"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema02@micropa_com"] <- "2"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema03@micropa_com"] <- "3"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema04@micropa_com"] <- "4"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema05@micropa_com"] <- "5"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema06@micropa_com"] <- "6"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema07@micropa_com"] <- "7"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema09@micropa_com"] <- "9"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema11@micropa_com"] <- "11"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema14@micropa_com"] <- "14"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema15@micropa_com"] <- "15"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema16@micropa_com"] <- "16"
uEMAComboFile$P_ID[uEMAComboFile$USER_ID == "uema19@micropa_com"] <- "19"

```


#### Run mixed effects ordinal regression with participant as random effect

```{r}
model1 <- clmm(ACTIVITY_ORDINAL~COUNTS_SUM_ANKLE_BEFORE + (1|USER_ID), data = uEMAComboFile, Hess = T, nAGQ = 1)

model1

summary(model1)
```


#### Ordinal regression with participant numneric ID
```{r}
model2 <- clmm(ACTIVITY_ORDINAL~COUNTS_LOG + (1|P_ID), data = uEMAComboFile, Hess = T, nAGQ = 10, control = clmm.control(maxIter = 50))

model2

summary(model2)
```

```{r}
library(car)
library(RVAideMemoire)
Anova(model2, type = "II")
```

#### Compare with fixed effects only model
```{r}
model.fixed <- clm(ACTIVITY_ORDINAL~COUNTS_LOG, data = uEMAComboFile)

anova(model2, null = model.fixed)
```

#### Nominal and scale tests
```{r}
nominal_test(model.fixed)

scale_test(model.fixed)
```

#### One way repeated - generalized linear model

```{r}

model_counts <- lmer(COUNTS_SUM_ANKLE_BEFORE~ACTIVITY_ORDINAL + (1 | P_ID), data = uEMAComboFile, REML = FALSE)
summary(model_counts)

coefs <- data.frame(coef(summary(model_counts)))
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs
```
```{r}
library(emmeans)
library(multcomp)
emmeans(model_counts, list(pairwise ~ ACTIVITY_ORDINAL), adjust = "tukey")


summary(glht(model_counts, linfct = mcp(ACTIVITY_ORDINAL = "Tukey")), test = adjusted("holm"))

```

#### With response time as a covariate

```{r}
uEMAComboFile$RESPONSE_TIME <- as.numeric(uEMAComboFile$RESPONSE_TIME)

model_counts <- lmer(COUNTS_SUM_ANKLE_BEFORE~ACTIVITY_ORDINAL + RESPONSE_TIME + (1 | P_ID), data = uEMAComboFile, REML = FALSE)
summary(model_counts)

coefs <- data.frame(coef(summary(model_counts)))
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs
```

```{r}
library(emmeans)
library(multcomp)
emmeans(model_counts, list(pairwise ~ ACTIVITY_ORDINAL), adjust = "tukey")


summary(glht(model_counts, linfct = mcp(ACTIVITY_ORDINAL = "Tukey")), test = adjusted("holm"))

```


#### Remove instances of "Vigorous activities"
```{r}
uEMANoVigorous <- uEMAComboFile[!uEMAComboFile$ACTIVITY_TYPE == "Vigorous", ]

levels(uEMANoVigorous$ACTIVITY_TYPE)
```

```{r}
model_counts_1 <- lmer(COUNTS_SUM_ANKLE_BEFORE~ACTIVITY_ORDINAL + (1 | P_ID), data = uEMANoVigorous, REML = FALSE)
summary(model_counts_1)

coefs <- data.frame(coef(summary(model_counts_1)))
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs
```

#### Pairwise comparisons

```{r}
library(emmeans)
library(multcomp)
emmeans(model_counts_1, list(pairwise ~ ACTIVITY_ORDINAL), adjust = "tukey")


summary(glht(model_counts_1, linfct = mcp(ACTIVITY_ORDINAL = "Tukey")), test = adjusted("holm"))
```

#### Pairwise comparisons

```{r}
model_counts <- lmer(COUNTS_LOG~ACTIVITY_ORDINAL + (1 | P_ID), data = uEMANoVigorous, REML = FALSE)
summary(model_counts)

coefs <- data.frame(coef(summary(model_counts)))
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs
```

```{r}
library(emmeans)
library(multcomp)
emmeans(model_counts, list(pairwise ~ ACTIVITY_ORDINAL), adjust = "tukey")


summary(glht(model_counts, linfct = mcp(ACTIVITY_ORDINAL = "Tukey")), test = adjusted("holm"))
```


#### Check the change in counts for vigorous activities:

```{r}
uEMAVigoroudOnly <- uEMAComboFile[uEMAComboFile$ACTIVITY_TYPE == "Vigorous", ]
uEMAVigoroudOnly
```

