---
title: "confusionMatrices"
author: "Aditya Ponnada"
date: "June 13, 2018"
output: html_document
editor_options: 
  chunk_output_type: inline
---

#### Import library

```{r}
library(psych)
library(MASS)
library(caret)
```


#### Select the columns of interest ...

```{r}
## read file

filePath = "C:/Users/Dharam/Downloads/microEMA/StudyFiles/CombinedData/tenSecMappedData.csv"

combinedFile <- read.csv(filePath, sep = ",", header = TRUE)

head(combinedFile)
tail(combinedFile)


### Remove NAs from the ankle before and after columns
combinedFile <- combinedFile[!is.na(combinedFile$COUNTS_SUM_ANKLE_BEFORE),]
combinedFile <- combinedFile[!is.na(combinedFile$COUNTS_SUM_ANKLE_AFTER),]

### Convert prompt time to date time object
combinedFile$PROMPT_TIME <- as.POSIXct(combinedFile$PROMPT_TIME, format = "%Y-%m-%d %H:%M:%OS")
```

## for ten seconds #####

#### Sedentary: [0.00, 330.1)
#### Light/Standing: [330.1, 1096.66)
#### Moderate/Walking: [1096.66, 2180.37)
#### Vigorous: [2180.37, 5400.00)



```{r}
combinedFile$COUNTS_ACTIVITY[combinedFile$COUNTS_SUM_ANKLE_BEFORE >= 0.00 & combinedFile$COUNTS_SUM_ANKLE_BEFORE < 330.01] <- "Sedentary"
combinedFile$COUNTS_ACTIVITY[combinedFile$COUNTS_SUM_ANKLE_BEFORE >= 330.01 & combinedFile$COUNTS_SUM_ANKLE_BEFORE < 1096.66] <- "Light/Standing"
combinedFile$COUNTS_ACTIVITY[combinedFile$COUNTS_SUM_ANKLE_BEFORE >= 1096.66 & combinedFile$COUNTS_SUM_ANKLE_BEFORE < 2180.37] <- "Moderate/Walking"
combinedFile$COUNTS_ACTIVITY[combinedFile$COUNTS_SUM_ANKLE_BEFORE >= 2180.37 & combinedFile$COUNTS_SUM_ANKLE_BEFORE < 5400.00] <- "Vigorous"


combinedFile$COUNTS_ACTIVITY <- as.factor(combinedFile$COUNTS_ACTIVITY)
```


```{r}
keep <- c("COUNTS_ACTIVITY", "ACTIVITY_TYPE")

sampleData <- combinedFile[keep]
```

#### Generate confusion matrix and plot the results ... 

```{r}
conf_mat_tab <- table(lapply(sampleData, factor))

matrixConf <- confusionMatrix(conf_mat_tab)

plot(matrixConf$table)
```

#### Display the results ...

```{r}
matrixConf
```

#### Get levels and their order
```{r}
levels(sampleData$COUNTS_ACTIVITY)
levels(sampleData$ACTIVITY_TYPE)
```

#### Convert levels to numerals i order
```{r}
# sampleData$COUNTS_CODED[sampleData$COUNTS_ACTIVITY == "Sedentary"] <- 1
# sampleData$COUNTS_CODED[sampleData$COUNTS_ACTIVITY == "Light/Standing"] <- 2
# sampleData$COUNTS_CODED[sampleData$COUNTS_ACTIVITY == "Moderate/Walking"] <- 3
# sampleData$COUNTS_CODED[sampleData$COUNTS_ACTIVITY == "Vigorous"] <- 4
# 
# sampleData$CODED_TYPE[sampleData$ACTIVITY_TYPE == "Sedentary"] <- 1
# sampleData$CODED_TYPE[sampleData$ACTIVITY_TYPE == "Light/Standing"] <- 2
# sampleData$CODED_TYPE[sampleData$ACTIVITY_TYPE == "Moderate/Walking"] <- 3
# sampleData$CODED_TYPE[sampleData$ACTIVITY_TYPE == "Vigorous"] <- 4



```


#### Get agreement (without within subject differences)

```{r}
library(irr)
kappa2(sampleData, "unweighted")
```

#### Sitting vs non sitting
```{r}
sample2 <- sampleData

levels(sample2$ACTIVITY_TYPE)[5] <- "Moving"
levels(sample2$COUNTS_ACTIVITY)[5] <- "Moving"

sample2$ACTIVITY_TYPE[!sample2$ACTIVITY_TYPE == "Sedentary"] <- "Moving"
sample2$COUNTS_ACTIVITY[!sample2$COUNTS_ACTIVITY == "Sedentary"] <- "Moving"

```

```{r}
kappa2(sample2, "unweighted")
```

```{r}
sample2Conf <- table(lapply(sample2, factor))

matrixConfSample2 <- confusionMatrix(sample2Conf)

plot(matrixConfSample2$table)

matrixConfSample2
```

#### Clubbing sedentary and standing together for ankle data
```{r}
sample3 <- sampleData

levels(sample3$ACTIVITY_TYPE)[5] <- "Moving"
levels(sample3$COUNTS_ACTIVITY)[5] <- "Moving"

sample3$ACTIVITY_TYPE[!(sample3$ACTIVITY_TYPE == "Sedentary" | sample3$ACTIVITY_TYPE == "Light/Standing")] <- "Moving"
sample3$ACTIVITY_TYPE[(sample3$ACTIVITY_TYPE == "Sedentary" | sample3$ACTIVITY_TYPE == "Light/Standing")] <- "Sedentary"
sample3$COUNTS_ACTIVITY[!(sample3$COUNTS_ACTIVITY == "Sedentary" | sample3$COUNTS_ACTIVITY == "Light/Standing")] <- "Moving"

sample3$COUNTS_ACTIVITY[(sample3$COUNTS_ACTIVITY == "Sedentary" | sample3$COUNTS_ACTIVITY == "Light/Standing")] <- "Sedentary"
```

```{r}
kappa2(sample3, "unweighted")
```
```{r}
sample3Conf <- table(lapply(sample3, factor))

matrixConfSample3 <- confusionMatrix(sample3Conf)

plot(matrixConfSample3$table)

matrixConfSample3
```
